---
title: "Sample Delineation - Fathers Analysis"
format: docx
editor: visual
execute:
  echo: false
  message: false
  warning: false
---

```{r setup}

# packages ----------------------------------------------------------------
packages <- c("tidyverse", "here", "gt")
groundhog_day <- "2024-01-11"

# (install and) load package versions available on the specified day to try
# to ensure reproducibility

library(groundhog)

groundhog::meta.groundhog(groundhog_day)

groundhog::groundhog.library(pkg = packages, date = groundhog_day)


library(here)
library(tidyverse)
library(gt)

dat_delineated <- readRDS(file = here::here("01_data-processing", "data_public", "delineation.RDS"))
```

We excluded the following couples:

1.  Fathers from the Baseline survey who were not in the national sample
2.  Mothers where the father of their child did not participate in the Baseline survey
3.  Mother-father pairs where fathers were in the two cities.
4.  Mother-father pairs where the father did not self-identify as either Black or White.
5.  Mother-father pairs who were not romantically involved at the Year 1 survey, or between the Year 1 and Baseline surveys.
6.  Mother-father pairs where the mother did not participate in the Year 1 survey and thus, her IPV victimisation, could not be ascertained.

The following table show the number of rows in our data that didn't meet each individual criterion.

```{r}
dat_delineated |>
  summarise(
    not_national_sample = sum(!(f_national_sample == 1)), 
    not_interviewed_zero = sum(!(f_interviewed_zero == 1)),
    not_two_cities = sum(!(f_two_cities == 1)), 
    not_race = sum(!(f_race == 1)),
    not_in_relationship = sum(!(m_in_relationship == 1)),
    not_interviewed_one = sum(!(m_interviewed_one == 1))
    
  ) |> 
  pivot_longer(
    cols = everything(),
    names_to = "criterion",
    values_to = "n_dont_fit"
  ) |> 
  gt::gt()
```

The following table shows the cumulative number of couples included and excluded based on applying each criterion successively:

```{r}
dat_delineated |> 
  dplyr::mutate(
    fit_criterion_1 = f_national_sample == 1,
    fit_criterion_2 = fit_criterion_1 & f_interviewed_zero == 1,
    fit_criterion_3 = fit_criterion_2 & f_two_cities == 1,
    fit_criterion_4 = fit_criterion_3 & f_race == 1,
    fit_criterion_5 = fit_criterion_4 & m_in_relationship == 1,
    fit_criterion_6 = fit_criterion_5 & m_interviewed_one == 1
  ) |> 
  dplyr::summarise(
    dplyr::across(
      .cols = starts_with("fit_"),
      .fns = ~sum(.x)
    )
  ) |> 
  pivot_longer(
    cols = everything(),
    names_to = "criterion",
    values_to = "n_cumulative_fit"
  ) |> 
  mutate(
    n_cumulative_dont_fit = nrow(dat_delineated) - n_cumulative_fit
  ) |> 
  gt::gt()
```

As we can see, our final sample included 1585 rows, meaning that 3313 couples were excluded based on the criteria.
